---
title: "3-report2"
output: html_document
---



Mass Communication Survey: Econometrics Analysis
========================================================

Q9) [Issues] Which important issues does your household need information on?
A9) Registration for official aid with UNHCR [Issues_REGISTRATION_UNHCR_registration]
- [Issues_REGISTRATION_UNHCR_registration] is a dummy variable that takes value “1” if refugee states he needs information on registering for official aid; takes value “0” if he states he does not need information on registering for official aid with UNHCR

QUESTION: What Information Sources are associated with the lowest “issues” for registration for official aid with UNHCR?


### Univariate Regressions:
 - On 17 variables with [Issues_REGISTRATION_UNHCR_registration] as dependent variable and “Information Source” as independent variables; a YES signifies the variable can explain at least 1% of the variation in [Issues_REGISTRATION_UNHCR_registration]

```{r}
#NO
reg1<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Television, datasetwcamp) 

#NO, but almost stat. sig. at 10%
reg2<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Mobile, datasetwcamp)

#N0  
reg3<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Internet_news, datasetwcamp) 

#N0
reg4<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Facebook, datasetwcamp) 

#N0
reg5<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Twitter, datasetwcamp) 

#N0, byt stat. sig. at 5%
reg6<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Notice_Board_or_Poster, datasetwcamp)

#NO
reg7<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Newspapers_or_Magazines, datasetwcamp)

#NO
reg8<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Leaflets, datasetwcamp)

#NO, but stat. sig. at 5%
reg9<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Radio, datasetwcamp)* 

#YES, and stat. sig. at 0.1%  
reg10<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Friends_and_Family, datasetwcamp)

#YES, and stat. sig. at 0.1%
reg11<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Community_Leaders, datasetwcamp)

#NO
reg12<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Religious_Institutions_Mosque_Church_etc, datasetwcamp)

#NO
reg13<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Jordanian_Government_Officials, datasetwcamp)

#NO, but stat sig. at 5%
reg14<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_UNHCR, datasetwcamp)

#NO
reg15<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Other_Humanitarian_Workers_NGOs_CBOs, datasetwcamp)

#NO, but stat. sig. at 14%
reg16<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Health_Centres_Schools_Community_Centres, datasetwcamp) 

#NO
reg17<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Short_film_video_clip, datasetwcamp)

#NO
reg18<-lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_other, datasetwcamp)


```

**Comment:** in italics are variables selected for model. Multivariate regressions with 7, 6 and 5 explanatory variables were estimated. Information Source UNHCR and Information Source Health Centers Schools Community Centers were excluded from the final model (here below) as found highly statistically insignificant when controlling for the other Information Source covariates.


### Multivariate Regression (full dataset; 5 variables):
```{r}
regFD <- lm(Issues_REGISTRATION_UNHCR_registration ~
              InformationSource_Radio +
              InformationSource_Friends_and_Family+InformationSource_Community_Leaders +
              InformationSource_Mobile +
              InformationSource_Notice_Board_or_Poster,
            datasetwcamp)

```

#**Comment:** Information Sources “Friends and Family”, “Community Leaders” and "Radio" are negatively 
associated with Need of Information for Official Aid Registration. Thus, if Friends and Family and/or 
Community Leaders and/or Radio is the Information Source, refugees are a lot less likely to need information on how to register for official aid with UNHCR. 

**Trust in Information Sources:**
- Radio: too many NA’s in data
- Friends and Family: most answers reflect “full” and “moderate” trust
- Community Leaders: most answers reflect “moderate” trust
- Mobile: most answers reflect “full” trust
- Notice Board or Poster: too many NA’s in data

**Comment:** Information Sources found statistically significant in regression are trusted.

*Tests:**
```{r}
#approx. 1% hence multicollinearity not an issue
vif(regFD) 

#no evidence of model mis-specification
resettest(regFD) 

coefs<-names(coef(regFD)) 

#the above unrestricted model is fine
linearHypothesis(regFD,coefs[-1],white.adjust="hc0") 
```

### Multivariate Regression (subsets; 5 variables):

**Female and Male Principal Representative of Household Subset Regressions:**
```{r}

regSF <- lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Radio + 
              InformationSource_Friends_and_Family +
              InformationSource_Community_Leaders +
              InformationSource_Mobile + 
              InformationSource_Notice_Board_or_Poster, 
            subset(datasetwcamp,pa_gender=="female"))

regSM <- lm(Issues_REGISTRATION_UNHCR_registration~InformationSource_Radio +
              InformationSource_Friends_and_Family +
              InformationSource_Community_Leaders +
              InformationSource_Mobile +
              InformationSource_Notice_Board_or_Poster, subset(datasetwcamp,pa_gender=="male"))

```
**Comment::** loss in predictive power in Female model; positive and negative associations remain 

unaltered (except Mobile in Female model, but highly statistically insignificant)

**Further Analysis on Gender Principal Representative of Household:**

```{r}

missue<-datasetwcamp[pa_gender=="male",105]
 #Average value of [Issues_REGISTRATION_UNHCR_registration] (need for information on official registration) 
#for female-only principal representative of household subset = 0.395
mean(missue)

fissue<-datasetwcamp[pa_gender=="female",105]
#Average value of [Issues_REGISTRATION_UNHCR_registration] (need for information on official registration) 
#for male-only principal representative of household subset = 0.422
mean(fissue) 

#Log-differences between PA_female and Registration Issues and PA_male and Registration Issues is = 0.067
log(mean(missue)) - log(mean(fissue)) 

```

**Comment:** on average households with a male principal representative have more issues on finding information on how to register for official aid with UNHCR, there is a gender gap of almost 7%.


**Camp and Non-Camp (Host) Subset Regressions:**

```{r}
regSC <- lm(Issues_REGISTRATION_UNHCR_registration ~
              InformationSource_Radio +
              InformationSource_Friends_and_Family +
              InformationSource_Community_Leaders +
              InformationSource_Mobile+InformationSource_Notice_Board_or_Poster,
            subset(datasetwcamp,Camp=="1"))

regSH <- lm(Issues_REGISTRATION_UNHCR_registration
            ~InformationSource_Radio +
              InformationSource_Friends_and_Family +
              InformationSource_Community_Leaders +
              InformationSource_Mobile+InformationSource_Notice_Board_or_Poster, subset(datasetwcamp,Camp=="0"))
```

**Comment**: in the camp-only data there is stronger explanatory power than in the full dataset for variables "Friends and Family" and "Comminity Leaders", but less for "Radio"; loss of predictive power in host-only data


### Limitations:
Regression models have a low Coefficient of Determination, they can therefore explain little of what is happening in Registration Issues given the explanatory variables chosen; this is normal as we regressed only dummy variables.




Inference to develop strategies
========================================================
  Is there a relation between the type of communication needs and the type of communication channel?


Before we go further with our analysis, we set null and alternate hypothesis. 
H_0 -  There is no correlation between communication needs and communication channel
H_A -  There is a correlation between communication needs and communication channel

since our variables are categorical, we will employ anova function to test our hypothesis.

we will check the condition for anova, 
1) sampled observations within group are independent.
2) groups are independent of each other.
3) distributions with in each group are nearly normal.
4) each group has roughly equal variability as you can see in the box plot.

since all the condition for anova has been met we will use aov function now.

```{r}

fit <- aov(consolidated.table$commneed ~ consolidated.table$commchannel, data = consolidated.table)
anova(fit)
```


from the result we reject null hypothesis and conclude that all group means are not equal.
now to check which group means are significantly different from each other we use Tukey test

```{r}
TukeyHSD(fit)
```
from the result we observe that all the group differ significantly from each other. Tukey test also gives the 95% confident interval difference between any two group.
we will interpret one result from Tukey output:
  
  Conclusion
========================================================
  
  Preferred communication channels are TV



Reference
========================================================
  
  ```{r}
names(data) # show the variables
str(data) # show the structure of the data
```