Analysis of Communication Survey
========================================================
  
  The "refugee communication survey" has been developped by UNHCR Jordan. The goals were:
  - Establish a baseline to measure future achievements of our communication strategy
- Establish coordination opportunities
- Define priorities in terms of needs and interventions.

The survey has three major parts
1. Communication needs: Establish main topics where there’s a lack of information (document, assistance, legal support, etc.) and the possible reasons for the gaps
2. Communication channels: Define  used channel (mobile, tv, radio, net, social networks, leaflet..) , how often they are used and how far they are trusted
3. Feedback mechanism: Assess existing feedback system and how they can be improved

A sample of **428 respondents** has been randomly selected both in camps and urban environment.

This document presents both the results and the R script developped in Rstudio (http://www.rstudio.com/) to obtain those results. Some good introduction to R here : https://github.com/DataScienceSpecialization/courses


Data preparation
========================================================
  
  Data were recorded in LimeSurvey and were extracted in the R format. Limesurvey allows for the creation of a file defining the syntax of the dataset.

```{r}
# RGet all data frame generated int he previous analysis phase
source("analysis.R")

```


The total number of valid observations is  **399**. This means that our sample is offering **more than 95 % confidence level**.

Look at the profile
========================================================
  
  We can then have a look at the profile of the respondant looking at the main characteristic we recorded:
  - Age Cohort
- Gender of the respondant
- Usge of smartphone
- Accomodation type

```{r}
library(vcd)

# Regression on Smartphone Vs Age & Gender
cotabplot(Freq ~Ac_SmartPhone + pa_agecohort | pa_gender, data=dataclean,
          panel=cotab_sieve, gp=shading_Friendly,
          labeling=labeling_values)

# Regression on Smartphone Vs Age & Accomodation
cotabplot(Freq ~Accom + Ac_SmartPhone | pa_gender, data=dataclean,
          panel=cotab_sieve, gp=shading_Friendly,
          labeling=labeling_values, margins = rep(1, 4), layout = NULL,
          text_gp = gpar(fontsize = 12), rect_gp = gpar(fill = grey(0.9)),
          pop = TRUE, newpage = TRUE)
```

Reshaping data
========================================================
  
  
```{r}
library(reshape)
library(ggplot2)
library(RColorBrewer)


```



1. What are the main Communication needs?
========================================================
  
  ```{r}
# Bar graph based on reordered variable per value
ggplot(data=dataclean.commtopic, aes(x=reorder(variable, value) , y=value, fill=variable)) + 
  geom_bar( stat="identity") + 
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication Topics") + ylab("Individual") +
  ggtitle("Main Information Topics")
```



2. What are the main communication channels?
========================================================
  ```{r}
# Bar graph based on reordered variable per value
ggplot(data=dataclean.channel, aes(x=reorder(variable, value) , y=value, fill=variable)) + 
  geom_bar( stat="identity") + 
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication channel") + ylab("Individual") +
  ggtitle("Main Information Source")
```
**Comment:** Among the various options, a few communication channels appeared to be largely preferred by refugees.


We can now look at the distribution of the communication channels according to other Variables
```{r}
# Reorder Variable per Value
dataclean.channel <- transform(dataclean.channel, variable=reorder(variable, -value) ) 

# Generation of pivot table and plotting
dataclean.infosourcepergender <- cast(dataclean.channel, pa_gender~variable, sum)
par(las=2)# make label text perpendicular to axis
barplot(as.matrix(dataclean.infosourcepergender),
        main="Information Source per Gender of Respondant",
        legend = levels(dataclean.channel$pa_gender),
        cex.names=0.9) 
```

**Comment:** In general, it seems that communication linked through new technology is occuring more for Male than Female

```{r}
dataclean.infosourcepersmartphone <- cast(dataclean.channel, Ac_SmartPhone~variable, sum)
par(las=2)# make label text perpendicular to axis
barplot(as.matrix(dataclean.infosourcepersmartphone),
        main="Information Source  Per owner of smartphones",
        legend = levels(dataclean.channel$Ac_SmartPhone),
        cex.names=0.9)
```

**Comment:** As expected, the distribution of smartphone seems to be correlated to the type of communication channel.
```{r}
dataclean.infosourceperage <- cast(dataclean.channel, pa_agecohort~variable, sum)
par(las=2)# make label text perpendicular to axis
barplot(as.matrix(dataclean.infosourceperage),
        main="Information Source  Per Age Cohort",
        legend = levels(dataclean.channel$pa_agecohort),
        cex.names=0.9)
```

**Comment:** An interesting pattern is that eldern report more than other the usage of direct communication with UN staff as a communication channel.
```{r}
dataclean.infosourceperaccom <- cast(dataclean.channel, Accom~variable, sum)
par(las=2)# make label text perpendicular to axis
barplot(as.matrix(dataclean.infosourceperaccom),
        main="Information Source  Per Accommodation type",
        legend = levels(dataclean.channel$Accom),
        cex.names=0.9)
```
**Comment:**  As expected, the usage of internet is not available to refugees living in tent and caravan.


```{r}

# Bar graph based on reordered variable per value
ggplot(data=dataclean.television, aes(x=variable , y=value, fill=variable, position="stack")) + 
  geom_bar( stat="identity") +
  #  geom_text(aes(label=variable), vjust=0) +
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication channel") + ylab("Individual") +
  ggtitle("Trust in TV as a communication channel")


# Bar graph based on reordered variable per value
ggplot(data=dataclean.mobile, aes(x=variable , y=value, fill=variable, position="stack")) + 
  geom_bar( stat="identity") +
  #  geom_text(aes(label=variable), vjust=0) +
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication channel") + ylab("Individual") +
  ggtitle("Trust in Mobile as a communication channel")



# Bar graph based on reordered variable per value
ggplot(data=dataclean.internet, aes(x=variable , y=value, fill=variable, position="stack")) + 
  geom_bar( stat="identity") +
  #  geom_text(aes(label=variable), vjust=0) +
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication channel") + ylab("Individual") +
  ggtitle("Trust in Internet as a communication channel")



# Bar graph based on reordered variable per value
ggplot(data=dataclean.friends, aes(x=variable , y=value, fill=variable, position="stack")) + 
  geom_bar( stat="identity") +
  #  geom_text(aes(label=variable), vjust=0) +
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication channel") + ylab("Individual") +
  ggtitle("Trust in Friends as a communication channel")


```


- What are the main Communication channels (with a breakdown of usage)?
- What are the main Communication channels (with a breakdown of trust)?



- What are the main communication needs(with a breakdown of satisfaction)?
- What are the main communication needs(with a breakdown of access problem)?



- Are refugees using complaint mecanism?
```{r}
# Bar graph based on reordered variable per value
# Bar graph based on reordered variable per value
ggplot(data=dataclean, aes(x=535 , y=12, fill=535)) + 
  geom_bar( stat="identity") + 
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication channel") + ylab("Individual") +
  ggtitle("Does complain")
```
```
- What are the issues refugees complained about?
- How complaint were emitted?



Inference to develop strategies
========================================================
  Is there a relation between the type of communication needs and the type of communication channel?


Before we go further with our analysis, we set null and alternate hypothesis. 
H_0 -  There is no correlation between communication needs and communication channel
H_A -  There is a correlation between communication needs and communication channel

since our variables are categorical, we will employ anova function to test our hypothesis.

we will check the condition for anova, 
1) sampled observations within group are independent.
2) groups are independent of each other.
3) distributions with in each group are nearly normal.
4) each group has roughly equal variability as you can see in the box plot.

since all the condition for anova has been met we will use aov function now.

```{r}

fit <- aov(dataclean$commneed ~ dataclean$commchannel, data = dataclean)
anova(fit)
```


from the result we reject null hypothesis and conclude that all group means are not equal.
now to check which group means are significantly different from each other we use Tukey test

```{r}
TukeyHSD(fit)
```
from the result we observe that all the group differ significantly from each other. Tukey test also gives the 95% confident interval difference between any two group.
we will interpret one result from Tukey output:
  
  Conclusion
========================================================
  
  Preferred communication channels are TV



Reference
========================================================
  
  ```{r}
names(data) # show the variables
str(data) # show the structure of the data
```