---
  title       : Mass Communication Survey - Jordan - 2014
subtitle    : An analysis of refugee communication needs, channel and usage
author      : UNHCR / REACH
job         : 
  framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
  
  ## Objective of the survey 
  
  The "refugee communication survey" has been developped by UNHCR Jordan. The goals were:
  > - Establish a baseline to measure future achievements of our communication strategy
> - Establish coordination opportunities
> - Define priorities in terms of needs and interventions.


---
  
  ##  Content of the survey
  
  2 samples (of 400 respondants each) were randomly selected  in both camp and urban environment.

> -  1. Communication needs: Establish main topics where there’s a lack of information (document, assistance, legal support, etc.) and the possible reasons for the gaps
> -  2. Communication channels: Define  used channel (mobile, tv, radio, net, social networks, leaflet..) , how often they are used and how far they are trusted
> -  3. Feedback mechanism: Assess existing feedback system and how they can be improved



---
  
  
  
  ## What are the main Communication needs?
  (based on urban sample)

```{r echo = F, results = 'asis'}

# Bar graph based on reordered variable per value
ggplot(data=dataclean.commtopic, aes(x=reorder(variable, value) , y=value, fill=variable)) + 
  geom_bar( stat="identity") + 
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication Topics") + ylab("Individual") +
  ggtitle("Main Information Topics")
```


---
  
  ## What are the main communication channels?
  (based on urban sample)
```{r echo = F, results = 'asis'}
# Bar graph based on reordered variable per value
ggplot(data=dataclean.channel, aes(x=reorder(variable, value) , y=value, fill=variable)) + 
  geom_bar( stat="identity") + 
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication channel") + ylab("Individual") +
  ggtitle("Main Information Source")
```


---
  
  ## Information Source per Gender of Respondant
  (based on urban sample)
```{r echo = F, results = 'asis'}
# Reorder Variable per Value
dataclean.channel <- transform(dataclean.channel, variable=reorder(variable, -value) ) 
# Generation of pivot table and plotting
dataclean.infosourcepergender <- cast(dataclean.channel, pa_gender~variable, sum)
par(las=2)# make label text perpendicular to axis
barplot(as.matrix(dataclean.infosourcepergender),
        main="",
        legend = levels(dataclean.channel$pa_gender),
        cex.names=0.9) 
```


---
  
  ## Information Source  Per owner of smartphones
  (based on urban sample)
```{r echo = F, results = 'asis'}
dataclean.infosourcepersmartphone <- cast(dataclean.channel, Ac_SmartPhone~variable, sum)
par(las=2)# make label text perpendicular to axis
barplot(as.matrix(dataclean.infosourcepersmartphone),
        main="",
        legend = levels(dataclean.channel$Ac_SmartPhone),
        cex.names=0.9)
```
---
  
  ## Information Source  Per Age Cohort
  (based on urban sample)
```{r echo = F, results = 'asis'}
dataclean.infosourceperage <- cast(dataclean.channel, pa_agecohort~variable, sum)
par(las=2)# make label text perpendicular to axis
barplot(as.matrix(dataclean.infosourceperage),
        main="",
        legend = levels(dataclean.channel$pa_agecohort),
        cex.names=0.9)
```

---
  
  ## Information Source  Per Accommodation type
  (based on urban sample)
```{r echo = F, results = 'asis'}
dataclean.infosourceperaccom <- cast(dataclean.channel, Accom~variable, sum)
par(las=2)# make label text perpendicular to axis
barplot(as.matrix(dataclean.infosourceperaccom),
        main="",
        legend = levels(dataclean.channel$Accom),
        cex.names=0.9)
```

---
  ## Trust in TV as a communication channel
  (based on urban sample)
```{r echo = F, results = 'asis'}
# Bar graph based on reordered variable per value
ggplot(data=dataclean.television, aes(x=variable , y=value, fill=variable, position="stack")) + 
  geom_bar( stat="identity") +
  #  geom_text(aes(label=variable), vjust=0) +
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication channel") + ylab("Individual") +
  ggtitle("")
```
---
  
  ## Trust in Friends as a communication channel
  (based on urban sample)
```{r echo = F, results = 'asis'}
# Bar graph based on reordered variable per value
ggplot(data=dataclean.friends, aes(x=variable , y=value, fill=variable, position="stack")) + 
  geom_bar( stat="identity") +
  #  geom_text(aes(label=variable), vjust=0) +
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication channel") + ylab("Individual") +
  ggtitle("")

```

---
  
  ## Trust in Internet as a communication channel
  (based on urban sample)
```{r echo = F, results = 'asis'}

# Bar graph based on reordered variable per value
ggplot(data=dataclean.internet, aes(x=variable , y=value, fill=variable, position="stack")) + 
  geom_bar( stat="identity") +
  #  geom_text(aes(label=variable), vjust=0) +
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication channel") + ylab("Individual") +
  ggtitle("")

```

---
  
  ## Trust in Mobile as a communication channel
  (based on urban sample)
```{r echo = F, results = 'asis'}
# Bar graph based on reordered variable per value
ggplot(data=dataclean.mobile, aes(x=variable , y=value, fill=variable, position="stack")) + 
  geom_bar( stat="identity") +
  #  geom_text(aes(label=variable), vjust=0) +
  guides(fill=FALSE) + coord_flip()+
  xlab("Communication channel") + ylab("Individual") +
  ggtitle("")
```
---
  ##  Respondant profile
  Smartphone Vs Age & Gender (based on urban sample)
```{r echo = F, results = 'asis'}
library(vcd)
cotabplot(Freq ~Ac_SmartPhone + pa_agecohort , data=dataclean,
          panel=cotab_sieve, gp=shading_Friendly,
          labeling=labeling_values)

```
---
  ##  Respondant profile 
  Smartphone Vs  Accomodation  (based on urban sample)
```{r echo = F, results = 'asis'}
library(vcd)
cotabplot(Freq ~Ac_SmartPhone + Accom  , data=dataclean,
          panel=cotab_sieve, gp=shading_Friendly,
          labeling=labeling_values, margins = rep(1, 4), layout = NULL,
          text_gp = gpar(fontsize = 12), rect_gp = gpar(fill = grey(0.9)),
          pop = TRUE, newpage = TRUE)
```
---
  ##  Respondant profile 
  Smartphone Vs Gender  (based on urban sample)
```{r echo = F, results = 'asis'}
library(vcd)
cotabplot(Freq ~Ac_SmartPhone + pa_gender , data=dataclean,
          panel=cotab_sieve, gp=shading_Friendly,
          labeling=labeling_values, margins = rep(1, 4), layout = NULL,
          text_gp = gpar(fontsize = 12), rect_gp = gpar(fill = grey(0.9)),
          pop = TRUE, newpage = TRUE)
```
---
  ##  Nex step in Analysis 
  
  
  > -  1. Compare results in camp and urban environement
> -  2. Analyse feedback mechanism 
> -  3. Is there a relation between the type of communication needs and the type of communication channel?